A quantitative framework for investigating the reliability of empirical network construction

### 2018-11-29 manuscript/CI_interactions.tex
reframing going well

    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}). Either style of model might be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. To provide another option for empiricists wishing to address the uncertainty in their networks, we propose a simple Bayesian framework that can easily be adapted to include whatever appropriate prior knowledge is available. This framework is designed to make the assumptions used when building networks more explicit and to quantify our uncertainty around each interaction in a network.

    First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but usually not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled willow-galler network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred, but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Do they interact?" and "Do we observe the interaction?" (Fig.~\ref{conceptual_fig}).

        \subsubsection*{Could the species interact under ideal conditions?}

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{}. These examples show that we often cannot say that an interaction absolutely does not occur. Instead, an unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing an interaction network found at several study sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they co-occur and interact elsewhere~\citep{}. We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction did not occur and when it occurred but was not observed.

          This phenomenon of interaction contingencies is usually not considered in network studies, but there is a rich literature in community ecology  on the topic. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} are just some of the factors contributing to variation in the frequency of interactions between a given pair of species. Some of these factors can be addressed in mesocosm studies of networks (e.g., environmental conditions can be held stable) or could be included in models along the line of trait-matching models (e.g., phenological matching). Expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will also help to reduce uncertainty if resource constraints permit. As long as researchers wish to sample empirical networks subject to changing conditions, however, it is not likely that they will be able to eliminate all uncertainty about whether or not pairs of species will interact during a given sampling period.

          Some models attempt to eliminate the sources of variation above by sampling intensively over a short time, during which probabilities of interaction are assumed to be constant~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. Any remaining variation in the interactions observed is therefore assumed to be due to detection uncertainty. This assumption may be accurate for some systems where the environment is relatively constant, there is little intraspecific variation in traits or preferences, etc. In most systems, and for any effort to compile a metaweb that will apply over broader spatial and temporal scales, probabilities of interaction are likely to vary during sampling.

@@

            Both of the above sources of uncertainty (i.e., whether species would be able to interact given their traits and whether they are able to interact at a particular place and time) are addressed in the concept of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

        \subsubsection*{Detection uncertainty}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). Some types of interactions will have higher detection uncertainty than others (e.g., pollination or predation often take place very quickly while parasitism can last for months or years). Even long-term interactions, however, can be missed, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities likely vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

      To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction. Similarly, bad weather can make interactions such as pollination less likely by reducing pollinator activity~\citep{}. For those pollinators which do venture forth in poor conditions, bad weather might also  increase detection uncertainty through reduced visibility or if pollinators make shorter trips.

    \subsection*{Estimating uncertainty}

        An observed interaction indicates that an interaction was feasible, occurred during sampling, and was detectable ($L = 1$, $X = 1$, and $D = 1$). An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$) and it is not usually possible to identify the source in empirical data. Only the case where $L = 0$ is an interaction that never occurs --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{conceptual_fig}). An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        [[move to box
        The obvious rule of thumb to reduce uncertainty is ``sample more". Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. [[Suggest combining approaches for better results - Jordano2016?]] ]]

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting should they ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. 
        Indeed, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Jordano2016}.
        To supplement repeated sampling efforts and reduce uncertainty around unobserved interactions, we suggest researchers use prior knowledge of the same or similar systems. Here, we outline a Bayesian approach to combining repeated sampling and prior knowledge in order to assemble a metaweb. We then demonstrate this approach using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a metaweb allows us to establish confidence intervals around measures of network structure.

@@

    We can create a simple Bayesian approach to modelling the probability of observing an interaction ($\lambda$) by combining a maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:

@@

    Combining this prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details). The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).

@@

    \subsubsection*{Choosing a prior distribution}  [[expand]]
      [[expand]]

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters and may be chosen to obtain an intentionally uninformative prior or derived using prior information to create an informed or empirical prior. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree distributions, or trait-matching functions (see \emph{Appendix S3} for details and a simple quantitative example).

      It is important to ensure that an informative prior accurately reflects the focal  system. For example, if the system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species and a set of closely-related insects. The similarity of traits across genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species mean that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species as aggregated nodes are likely to have more interaction partners than single species.

      The choice of prior will depend on the information available and the question of interest. In general, it is best to use a prior taken from a similar system as emphasised above. If such data are not available, a prior based on many networks with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions. Similarly, if detailed information is available but refers to the question at hand, it is best to use a less informative prior so as not to force a particular result. For example, if researchers are interested in testing whether body-size ratios affect probabilities of interaction they should not use a prior which predicts interactions based on body sizes.

@@

        An uninformative prior is chosen so as not to bias the posterior distribution in any particular direction. That is, all of the information will come from the observed data. For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair. Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prios: a beta distribution with $\alpha$=$\beta$=0.5. The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation. An uninformative prior is most appropriate when considering a novel system or a system where the only prior knowledge available directly relates to the question we wish to analyse.

      \textbf{Informed priors}

        In most cases, researchers will be able to draw upon prior knowledge for at least some interactions. One very simple example is the assumption that, in a food web, plants will not consume any prey. There is very little uncertainty around the lack of a observed predation of any plant upon any animal in the system, regardless of how often the plant and animal are observed together.

        [[addressing different types of uncertainty]]
        [[drawing upon system-specific or broader knowledge]]

        If we are interested only in interactions which occur in the focal system under current environmental conditions, we might use a prior which includes probabilities of co-occurrence. That is, we could limit the set of potential interactions to pairs of species which currently co-occur, condition probabilities of interaction on probabilities of co-occurrence based on abundance or microhabitat use, etc.~\citep{Gravel2013,Weinstein2017} Note that such models lump together the questions of whether species can interact and whether they interact at a particular site and are only concerned with measuring detection uncertainty. Whether or not this is appropriate will depend upon the question of interest.

        If traits governing interactions are known (e.g., body size in food webs~\citep{Gravel2013} or corolla depth in pollination networks~\citep{Weinstein2017a}), then trait-based models may be used as a prior. Such models estimate whether a pair of species \emph{can} interact, regardless of whether they are likely to encounter each other (although encounter probabilities and abundances can also be included, as in~\citet{Graham2018}). To address both multiple sources of uncertainty, a researcher might combine trait-based and co-occurrence models into a single prior. Such a model would reduce the uncertainty about unobserved interactions, but at the cost of adding more assumptions about the study system. This type of very detailed prior is therefore most appropriate in very well-understood systems where a great deal of expert knowledge can be applied, or in systems which are believed to follow general rules of, for example, allometric scaling~\citep{Gravel2013}. Where there is less system-specific prior knowledge, we can use prior models based on general trends in allometric scaling~\citep{Riede2011,Gravel2013}.

        An informed prior could be based on one or a few traits, as those described above, or it could incorporate a great deal of information about co-occurrence and encounter probabilities, forbidden links, etc.~\citep{Jordano2016}. Importantly, the complexity of a prior model depends both on the information available and on the question of interest. If researchers wish to test for an effect of body mass ratios on interaction probabilities, for example, they should not include body mass in their prior. Including a trait in a prior means assuming that trait has an effect on which interactions we detect and it is therefore inappropriate to test for such an effect in the same study.

        The relevant traits and degree of trait-matching between interaction partners is likely to vary between systems~\citep{Gravel2013,Weinstein2017a}. We therefore urge caution when using a model developed for one system as the prior for another. 
        See \emph{Appendix S3} for a simple quantitative example using degree distributions to obtain $\alpha$ and $\beta$.

      \textbf{Empirical priors} [[using data from the data in question]][[contentious]][[should these be drawn from hyperpriors or fixed for each interaction]]

>>>>

    [[These two paragraphs try to frame our study more clearly. Any help to shorten them?]]
    To date, models incorporating uncertainty have either been very general (e.g.,~\citet{Guimera2009,Gravel2013}) or very system-specific (e.g.,~\citet{Bartomeus2013,Weinstein2017,Weinstein2017a,Graham2018}); in either case one of these models may be a poor fit for a particular study system. Moreover, some of the system-specific models described above cannot accommodate species observed only once~\citep{Bartomeus2013,Weinstein2017}. As rare species are likely to be observed less frequently~\citep{Bluthgen2010} and may be of particular interest (e.g., when modelling species loss), there is a need for a more widely-applicable framework that includes such rare species.

    Here we introduce a simple Bayesian framework that can easily be adapted to different systems. First, we provide a brief description of the nested levels of uncertainty affecting ecological network construction. In the context of this uncertainty, which can be reduced but not eliminated by high-quality sampling (\citealp[see Box 1]{Bartomes2013}), we present our Bayesian framework for combining observed data with a prior expectation of network structure. We conclude with a worked example applying this framework to an intensively-sampled willow-galler network. We find that even the highest-quality empirical network we could find had substantial uncertainty about whether many pairs of species interact, demonstrating the need to include information about this uncertainty in published networks. We also show that this interaction-level uncertainty leads to uncertainty about estimates of network structure, with important implications for comparisons across networks; especially those compiled with different sampling intensity~\citep{Weinstein2017}.

@@

      We start from the perspective of a community ecologist faced with the task of describing a previously unknown interaction network. This ecologist will be interested in generating a description of the species/nodes present and the links between them~\citep{Roslin2016}.  Importantly, the information sought is conveyed by both the presence and \emph{absence} of links. Presences and absences are not, however, equally certain. An observed link definitely occurred (assuming we can correctly identify the species involved), but there are multiple reasons why a given link may not be observed \emph{whether or not the interaction truly occurred}. Moreover, given an unobserved interaction in an empirical dataset, we often cannot determine why the interaction did not occur \emph{post hoc}. The detection of any interaction is a stochastic process subject to many levels of uncertainty. As a conceptual guide to the factors affecting this process, we describe three nested levels of uncertainty that roughly address the questions: "Could species $i$ and $j$ interact?", "Did they interact?" and "Did we observe the interaction?" (Fig.~\ref{conceptual_fig}).

        \subsubsection*{Could the species interact?}

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi$ and $\lambda$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi$ will remain.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling~\citep{Jordano1987}, physiological constraints~\citep{Jordano1987,More2012}, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

        \subsubsection*{Did we observe all interactions that occurred?}

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.

          Some types of interactions will have higher detection uncertainty than others. Pollination, for example, occurs briefly and does not leave long-lasting evidence, while parasitism can be a lifelong association between species. Even long-term interactions can be missed, however, especially if species are difficult to identify or if not all individuals of a species share the interaction~\citep{Wells2013,Cirtwill2016}. Parasites, for example, are often concentrated in only a few individuals~\citep{Lagrue2017}. If these infected individuals do not happen to be included in a sample, their interactions will be missed. Detection probabilities also vary widely between species, and potentially individuals within species, due to different abundances and behaviours~\citep{Wells2013,Weinstein2017}.

    \subsection*{Can't we just sample more?}

        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

        When considering a metaweb, we wish to separate the unobserved interactions where $L = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C), thereby adding more zeros with high uncertainty (which would require more sampling to reduce, and so on).

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}. Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.

        In short, high-quality sampling is an essential component of ecological network construction and increasing sampling (length of time, number of sites, number of distinct methods, etc.) can reduce some of the uncertainty about unobserved interactions. We believe, however, that empirical researchers generally sample to the maximum extent possible given constraints of time, resources, and study sites. This practical constraint means that reducing one source of uncertainty is likely to increase another source (e.g., sampling intensively at a single site may reduce detection uncertainty but will increase uncertainty due to variation between sites). The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig.~\ref{upper_limits}), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}. For pairs of species with fewer observations, we can reduce uncertainty by combining the observed data available with prior knowledge about the system. This is straightforward to do using a Bayesian approach, as detailed below.

@@

    The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:

@@

    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Combining the prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details). The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).

@@

    \subsubsection*{Choosing a prior distribution}

      The choice of prior distribution will reflect the goal of a study, the amount of prior knowledge available, and the strength of researchers' belief in that prior knowledge. Note that there is no 'correct' prior as long as we do not know the true distribution of interaction probabilities~\citep{Spiegelhalter2000}. The goal is to select a reasonable prior that reflects our assumptions about the true distribution, and then adjust this prior with observed data as it becomes available. When in doubt, it is also possible to model interaction probabilities using a variety of priors and then compare results~\citep{Spiegelhalter2000}. Some researchers may be reluctant to adopt a Bayesian approach because of its perceived subjectivity (i.e., the metaweb we obtain will depend upon the assumptions used when developing a prior). We argue that one of the advantages of the Bayesian approach is that it makes some of the subjectivity inherent in network construction explicit. Researchers compiling empirical networks face many decisions about where to set community boundaries~\citep{}, the set of species to include in the focal community~\citep{}, what type of sampling is most appropriate~\citep{Wirta2014}, etc. All of these choices will affect the compiled network and most do not have clear answers, making all empirical networks (and all theoretical networks, which likewise depend upon the assumptions used in building the network) to some extent subjective. In addition, researchers distinguishing "forbidden links" inherently rely on prior knowledge to identify these links~\citep{Jordano2016}. Stating that an interaction is "forbidden" is, in effect, applying a very strong prior to reduce/eliminate uncertainty about the non-observation of that interaction. Given this reality, we feel it is better to make the assumptions used to build a network as explicit as possible so that these assumptions can be questioned, compared between studies, and tested.

@@

        If researchers wish to reflect uncertainty in their data without applying any particular assumptions/prior knowledge or account for the possibility that the distribution of probabilities of interaction may vary, they can select $\alpha$ and $\beta$ to produce an intentionally uninformative prior~\citep{Leyland2005,Berger2006}. This prior can then be given a low weight, such that any observed data will outweigh the prior distribution. For pairs of species with little or no observed data, an uninformative prior will leave large variance about $\lambda$ and reflect our lack of knowledge about the pair. Since we model $\lambda$ as a Bernoulli trial, the appropriate uninformative prior is Jeffreys prior: a beta distribution with $\alpha$=$\beta$=0.5. The sum of $\alpha$ and $\beta$ is roughly equivalent to the weight of the prior, so Jeffreys prior has equal weight to a single observation.

      \textbf{Informative priors}

        In most cases, we have at least some prior knowledge about a system which we can use to reduce uncertainty about interactions. One common example is the well-justified assumption that plants will not consume animals in a food web; excluding carnivorous plants it is not contentious to say that we have little to no uncertainty about unobserved links describing plants feeding on animals. Similarly, if we observe two species which are normally obligate mutualists co-occurring but not interacting, we would be very doubtful that a zero reflecting this interaction was true (i.e., high uncertainty about this zero). It is straightforward to extend the intuition behind these special cases to the full set of species in a network using trait-based models, as long as the traits likely to affect interaction probabilities are known (e.g.,~\citet{Riede2011,Gravel2013,Bartomeus2016,Weinstein2017}). Models for interaction probabilities could also include information on abundances, phenological matching, co-occurrence etc. as available~\citep{Jordano2016,Weinstein2017a,Graham2018}. This approach allows us to tailor the level of uncertainty surrounding each interaction based on the species involved but involves many assumptions about which parameters affect interaction probabilities and the strength and shapes of these relationships. There is, therefore, a risk of over-fitting with complicated trait-based models. Also note that researchers wishing to test whether a particular trait influences interaction probabilities should either exclude that trait from their prior or model the network using priors which include and exclude the trait of interest (as in~\citet{Weinstein2017,Weinstein2017a}).

        Alternatively, it is possible to develop a prior based on the properties of a set of published networks (i.e., "reference Bayes"~\citet{Spiegelhalter2000}). While this type of prior does not allow for the prior distribution to vary between species pairs, it relies on fewer assumptions about the forces structuring interaction probabilities. Instead, we assume only that the focal network will have similar structural properties to those of published networks. For example, connectance ($C=L/S^2$, where $L$ is the number of interactions and $S$ is the number of species) is available for many networks. The distribution of these connectances can be used to predict the distribution of interaction probabilities in a new network. If we know the mean $\overline{C}$ and variance $\sigma_C^2$ of a distribution of connectances, then the hyperparameters are:

        \begin{equation}
        \alpha = \overline{C}(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) ,
        \end{equation}

        \begin{equation}
        \beta = (1-\overline{C})(\frac{\overline{C}(1-\overline{C})}{\sigma_C^2}-1) .
        \end{equation}
